---
title: "Project"
author: "Ika"
date: "6/11/2020"
output: html_document
---

```{r }

print(getwd())

setwd("C:/Users/user/OneDrive/Documents/WIE2003/dataset/")

print(getwd())
```



```{r }
newData <- readxl("C:/Users/user/OneDrive/Documents/WIE2003/dataset/Clean Data USA.xlsx")
```

#### Result 1 : Comparisons between people who are self-employed and having family history of mental health.

We suspected that people who has mental health family history would prefer self-employment as it would have lessen their likeliness of being judge by the employers.

But based on the graph below, it is seen that employees with family history prefer to be employed by companies and etc. 
```{r}
##Question 1

library(ggplot2)
library(dplyr)
library(data.table)

#group the dataset by history and self employment
#create a table that stores all the data 
history_self<- newData %>%
  group_by(family_history,self_employed) %>%
  dplyr::summarize(Total=n())

#get the total frequency of self-employment in each state
data.table(history_self)

#shows comparison between people who are self-employed and having family history
#plotting bar graph
ggplot(history_self,aes(family_history,Total,fill=self_employed))+
  geom_bar(stat="identity") +
  geom_text(aes(label=Total), vjust=1.2, color="white", size=3.5) +
  ggtitle("Self-Employed vs Family History")

```

#### Result 2 : Region in USA that has the highest rate of self-employment.

As shown from the below, it can be seen that CA (California) has the highest rate of self-employment.

```{r }

#Question 4

#group the dataset by state and self_employed
#create a table that stores all the data 
state_self<- newData %>%
  group_by(state,self_employed) %>%
  dplyr::summarize(Total=n())

#get the total frequency of self-employment in each state
data.table(state_self)

#shows which region in USA has the highest rate of self-employment
#plotting bar graph
ggplot(state_self,aes(state,Total,fill=self_employed))+
  geom_bar(stat="identity", position=position_dodge())+
  ggtitle("Self Employment by State ")
```


#### Result 3 : Percentage of supervisor who discussed about mental issues with employees.

Based on the pie-chart the majority of employees (59.5%) will at least discuss to some of the supervisors if they experience mental issues

```{r}

#Question 5
library(scales)
#group the dataset by state and self_employed
#create a table that stores all the data 
sup<- newData %>%
  group_by(supervisor) %>%
  dplyr::summarize(Total=n())

#get the total frequency of self-employment in each state
data.table(sup)

#Declaring total overall
OT <- 751

#shows comparison between discussion with the supervisor
#plotting bar graph
ggplot(sup, aes(x="", y=Total, fill=supervisor))+
geom_bar(width = 1, stat = "identity") + 
coord_polar("y", start=0) +
theme(axis.text.x=element_blank()) +
geom_text(aes(y = Total/3 + c(0, cumsum(Total)[-length(Total)]), 
            label = percent(Total/OT)), size=5)

```








