
# My First Knit Document
This is a text ("Hello THere my Name is Ika")

## **Introduction**

### Codes that are echoed
```{r}
#code is echoed
set.seed(1)
x <- rnorm(100)
mean(x)
```
### Codes that are not echoed
_note: The code is the same as above but do not show the R_
```{r simulation, echo=FALSE}
#code is not echoed
set.seed(1)
x <- rnorm(100)
mean(x)
```
### Inline Text Computation
```{r}
time <- format(Sys.time(),"%a %b %d %X %Y")
rand <- rnorm(1)
```
The current time is `r time`. My fav random number is `r rand`.

### Incorporating Graphics

Stimulate data
```{r stimulatedata,echo=TRUE}
x <- rnorm(100);
y <- x + rnorm(100, sd = 0.5)
```

Here is the scatterplot of the data
```{r scatterplot,fig.height=4}
par(mar = c(5,4,1,1), las = 1)
plot(x,y,main = "My Stimulated Data")
```

### Making Tables

```{r fitmodel}
library(datasets)
data("airquality")
fit <- lm(Ozone ~ Wind + Solar.R, data = airquality)
```

Here is a table of regression coefficients.

```{r showtable,results='asis'}
library(xtable)
xt <- xtable(summary(fit))
print(xt,type = "html")
```

### Setting Global Options
```{r setoptions, echo=FALSE}
library(knitr)
knitr::opts_chunk$set
#statement above set default to NOT echo
opts_chunk$set(echo = FALSE, results = "hide")
```

First simulate data
```{r simulatedata, echo=TRUE} 
#statement above overides default
x <- rnorm(100);
y <- x + rnorm(100,sd = 0.5)
```

Here is a scatterplot of data.

```{r scaterplot,fig.height= 4}
par(mar = c(5,4,1,1), las = 1)
plot(x,y, main = "My Simulated Data")


